1) Which Employers send most number of H-1B visa applications? 

2) What is the Percentage share out of the 85,000 visa cap for the Employers with most applications?

3) Most common Job Titles and their Relative wages to Industry standard as well as absolute?

Let's begin the analysis by loading the libraries and the dataframe!

```{r}
library(dplyr)
library(ggplot2)
library(ggrepel)
library(ggmap)
source("helpers.R")
```
helpers.R includes a suite of plotting and filter functions that will help us with the data analysis. 


```{r}
h1b_df <- readRDS("h1b_transformed.rds")

colnames(h1b_df)
```

<h2> High-Applicant Employers </h2>

In this sub-section, I analyze employers with high number of applications. Let's begin by finding out the top 10 employers with the most number of applications in the period 2011-2016.

It might occur that Employer Names takes most of the space leaving almost little for the actual plot. For this purpose, I cut short Employer names to only the first word in their title. An another approach might be reducing the axis.text size for ggplot2.

```{r}
h1b_df$EMPLOYER_COMPACT = sapply(h1b_df$EMPLOYER_NAME,split_first,split = " ")
```
```{r}
input <- plot_input(h1b_df, "EMPLOYER_NAME", "YEAR", "TotalApps",filter = TRUE, Ntop = 10)

g <- plot_output(input, 'EMPLOYER_NAME','YEAR','TotalApps', 'EMPLOYER','TOTAL NO. of APPLICATIONS') + theme(axis.title = element_text(size = rel(1.5)),
          axis.text.y = element_text(size=rel(0.85),face="bold"))
g
```

Observations:

1. Infosys leads the pack by a huge margin with over 30000 applications in 2013 and 2015.

2. The Top 10 list is dominated by the Indian IT companies.

Next, let's look at the Percentage Share of the Approved/Certified H-1B applications for these top 10 employers out of the 85000 cap.

```{r}
g <- plot_output(input, 'EMPLOYER_NAME','YEAR','Share', 'EMPLOYER','% SHARE')

g
```

The assumption in this plot is that each certified H-1B application corresponds to a unique H-1B visa. Accordingly, if an employer's 8500 H-1B visa applications were certified then it's percentage share in the 85,000 visa cap is 10%. Based on this assumption, I make the following observations:

1. Over 90% of the certified H-1B visa applications belong to the IT companies with the most applications.

2. Infosys again takes a major share.


